Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-28 ms/SI.rmd
Fix names of references in SI table 1

---
title: ""
bibliography: "si_references.bib"
mainfont: Times New Roman.ttf
fontsize: 12pt
mainfontoptions: 
- BoldFont=Times New Roman Bold.ttf
- ItalicFont=Times New Roman Italic.ttf
- BoldItalicFont=Times New Roman Bold Italic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
nocite: | 
  @NMNS2008, @Copeland1932, @FloraNSW2019, @Brownsey1987, @Murdock2003, @Nayar1971, @Lloyd1980, @Zhang2008, @Bierhorst1967, @Martin2006, @Tigerschiold1989, @Tigerschiold1990, @Atkinson1975, @Chen2014a
---

@@

Article title: Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns

@@

'taxon code' is the name used for that taxon in analyses (see Table S1). For data source, L = lab observation of gametophyte cultured from spore, F = field observation of gametophyte subsequently identified using DNA barcoding, T = morphology inferred based on taxonomy, M = measurement of a field-collected specimen; cited references provided at end of SI.

>>>>

---
title: ""
bibliography: "si_references.bib"
mainfont: Times New Roman.ttf
fontsize: 12pt
mainfontoptions: 
- BoldFont=Times New Roman Bold.ttf
- ItalicFont=Times New Roman Italic.ttf
- BoldItalicFont=Times New Roman Bold Italic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
nocite: | 
  @NMNS2008, @Copeland1932, @FloraNSW2019, @Brownsey1987, @Murdock2003, @Nayar1971, @Lloyd1980, @Zhang2008, @Bierhorst1967, @Martin2006, @Tigerschiold1989, @Tigerschiold1990, @Atkinson1975, @Palmer2003
---

@@

Article title: Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

@@

Continuous measurements shown as mean, standard deviation (sample size). 'taxon code' is the name used for that taxon in analyses (see Table S1). For data source, L = lab observation of gametophyte cultured from spore, F = field observation of gametophyte subsequently identified using DNA barcoding, T = morphology inferred based on taxonomy, M = measurement of a field-collected specimen; cited references provided at end of SI.
